Centralized Programming for Distributed Control Planes

### 2016-01-27 paper/compilation.tex
stashing changes
a few edits

     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
     p       &::=& t \mapsto r_1 \gg \dots \gg r_m & \textit{preferences} \\
     t       &::=& & \textit{test} \\
         &\BNFALT& true & \textit{true} \\
         &\BNFALT& \neg t & \textit{negation} \\
         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
         &\BNFALT& prefix = x & \textit{prefix test} \\
         &\BNFALT& comm = c & \textit{community test} \\
     r       &::=& & \textit{regular paths} \\
         &\BNFALT& n & \textit{AS number} \\
         &\BNFALT& in & \textit{internal loc} \\
         &\BNFALT& out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& !(r) & \textit{path negation} \\
         &\BNFALT& r^* & \textit{repetition} \\
     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
  \end{array} \]

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{\large Propane Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rcl}
    \hline
    any           & = & out^* \cdot in^+ \cdot out^* \\
    internal      & = & in^+ \\
    external      & = & out^+ \\
    only(X)       & = & any \cap X^* \\
    never(X)      & = & any \cap (!X)^* \\
    through(X)    & = & out^* \cdot in^* \cdot X \cdot in^* \cdot out^* \\
    after(X)      & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
    before(X)     & = & out^* \cdot in^+ \cdot out^* \cdot (X \cap out) \cdot out^* \\
    end(X)        & = & any \cap (\Sigma^* \cdot X) \\
    start(X)      & = & any \cap (X \cdot \Sigma^*) \\
    exit(X)       & = & (out^* \cdot in^* \cdot (X \cap in) \cdot out \cdot out^*) \cup \\
                  &        & (out^* \cdot in^+ \cdot (X \cap out) \cdot out^*) \\
    enter(X)      & = & (out^* \cdot out \cdot (X \cap in) \cdot in^* \cdot out^*) \cup \\
                  &        & (out^* \cdot (X \cap out) \cdot in^+ \cdot out^*) \\
    link(X,Y)     & = & any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
    path(\vec{X}) & = & any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
    novalley(\vec{X}) & = & any ~ \cap \\
                  &   & !path(X_2,X_1,X_2) ~ \cap \dots \cap \\
                  &   & !path(X_n,X_{n-1},X_n) \\
  \end{array} \]

>>>>

     pol     &::=& p_1, \dots, p_n & \textit{constraints} \\
     p       &::=& t \mapsto r_1 \gg \dots \gg r_m & \textit{preferences} \\
     t       &::=& true & \textit{true} \\
         &\BNFALT& \neg t & \textit{negation} \\
         &\BNFALT& t_1 \vee t_2 & \textit{disjunction} \\
         &\BNFALT& t_1 \wedge t_2 & \textit{conjunction} \\
         &\BNFALT& prefix = x & \textit{prefix test} \\
         &\BNFALT& comm = c & \textit{community test} \\
     r       &::=& n & \textit{AS number} \\
         &\BNFALT& in & \textit{internal loc} \\
         &\BNFALT& out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& !(r) & \textit{path negation} \\
         &\BNFALT& r^* & \textit{repetition} \\
     l       &::=& r_1 \rightarrow r_2 & \textit{link pairs} \\
     cc     &::=& agg(x, l) \BNFALT tag(c, t, l) & \textit{control constraints} \\
  \end{array} \]

  \end{minipage}
  %
  ~~
  \vrule
  ~~
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{\large Propane Expansions}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rcl}
    \hline
    any           & = & out^* \cdot in^+ \cdot out^* \\
    internal      & = & in^+ \\
    only(X)       & = & any \cap X^* \\
    never(X)      & = & any \cap (!X)^* \\
    through(X)    & = & out^* \cdot in^* \cdot X \cdot in^* \cdot out^* \\
    after(X)      & = & out^* \cdot (X \cap out) \cdot out^* \cdot in^+ \cdot out^* \\
    before(X)     & = & out^* \cdot in^+ \cdot out^* \cdot (X \cap out) \cdot out^* \\
    end(X)        & = & any \cap (\Sigma^* \cdot X) \\
    start(X)      & = & any \cap (X \cdot \Sigma^*) \\
    exit(X)       & = & (out^* \cdot in^* \cdot (X \cap in) \cdot out \cdot out^*) \cup \\
                  &        & (out^* \cdot in^+ \cdot (X \cap out) \cdot out^*) \\
    enter(X)      & = & (out^* \cdot out \cdot (X \cap in) \cdot in^* \cdot out^*) \cup \\
                  &        & (out^* \cdot (X \cap out) \cdot in^+ \cdot out^*) \\
    link(X,Y)     & = & any \cap (\Sigma^* \cdot X \cdot Y \cdot \Sigma^*) \\
    path(\vec{X}) & = & any \cap (\Sigma^* \cdot X_1 \dots X_n \cdot \Sigma^*) \\
    novalley(\vec{X}) & = & any ~ \cap \\
                  &   & !path(X_2,X_1,X_2) ~ \cap \dots \cap \\
                  &   & !path(X_n,X_{n-1},X_n) \\
  \end{array} \]

### 2016-01-27 paper/theory.tex
a few edits

Here we investigate the correctness and expressiveness properties of \sysname. We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures? (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?

>>>>

%Here we investigate the correctness and expressiveness properties of \sysname. We are mainly concerned with answering the following questions: (1) does the distributed, compiled policy faithfully implement the user's policy regardless of failures? (2) Are the resulting BGP configurations stable?, and (3) what polcies are or are not expressible in \sysname?
